---
title: "PhenoVision Reproductive Model Training Report"
author: "Generated by targets pipeline"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: hide
params:
  test_summary: NULL
  test_metrics: NULL
  optimal_thresholds: NULL
  conformal_coverage: NULL
  alpha_analysis: NULL
  alpha_analysis_positive: NULL
  alpha_analysis_negative: NULL
  alpha_analysis_factorial: NULL
  optimal_alpha_candidates: NULL
  factorial_analysis_file: NULL
  optimal_candidates_file: NULL
  training_config: NULL
  all_predictions: NULL
  plot_threshold_performance: NULL
  plot_conformal_positive: NULL
  plot_conformal_negative: NULL
  plot_conformal_coverage: NULL
  plot_factorial_ppv_flower: NULL
  plot_factorial_ppv_fruit: NULL
  plot_factorial_npv_flower: NULL
  plot_factorial_npv_fruit: NULL
  plot_factorial_accuracy_flower: NULL
  plot_factorial_accuracy_fruit: NULL
  plot_factorial_jindex_flower: NULL
  plot_factorial_jindex_fruit: NULL
  plot_factorial_dqi_flower: NULL
  plot_factorial_dqi_fruit: NULL
  plot_factorial_dataloss_flower: NULL
  plot_factorial_dataloss_fruit: NULL
  plot_factorial_det_dataloss_flower: NULL
  plot_factorial_det_dataloss_fruit: NULL
  plot_factorial_nondet_dataloss_flower: NULL
  plot_factorial_nondet_dataloss_fruit: NULL
  plot_conformal_pvalue_density: NULL
  plot_pareto_elbow: NULL
  plot_conformal_calibration_curve: NULL
  conformal_calibration_file: NULL
  recommended_alpha_file: NULL
  accuracy_buffer_flower_overall: NULL
  accuracy_buffer_flower_ppv_npv: NULL
  accuracy_buffer_fruit_overall: NULL
  accuracy_buffer_fruit_ppv_npv: NULL
  plot_equivocal_zone_combined: NULL
  plot_accuracy_buffer_flower: NULL
  plot_accuracy_buffer_fruit: NULL
  accuracy_buffer_results_file: NULL
  multi_cutoff_flower: NULL
  multi_cutoff_fruit: NULL
  plot_multi_cutoff_dataloss: NULL
  multi_cutoff_results_file: NULL
  test_evaluation_summary: NULL
  test_evaluation_file: NULL
  final_buffer_params_file: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 10,
  fig.height = 6
)

library(tidyverse)
library(knitr)
library(kableExtra)
library(patchwork)
```

## Executive Summary

This report summarizes the training and evaluation of the PhenoVision reproductive structures model (version **`r params$training_config$model_version`**).

### Key Results

```{r summary-table}
if (!is.null(params$test_summary)) {
  summary_df <- params$test_summary

  tibble(
    Metric = c("Test Set Size",
               "Flower Accuracy", "Flower DQI", "Flower J-Index", "Flower AUC",
               "Fruit Accuracy", "Fruit DQI", "Fruit J-Index", "Fruit AUC"),
    Value = c(
      format(summary_df$n_test, big.mark = ","),
      sprintf("%.2f%%", summary_df$flower_accuracy * 100),
      sprintf("%.4f", summary_df$flower_dqi),
      sprintf("%.4f", summary_df$flower_j_index),
      sprintf("%.4f", summary_df$flower_auc),
      sprintf("%.2f%%", summary_df$fruit_accuracy * 100),
      sprintf("%.4f", summary_df$fruit_dqi),
      sprintf("%.4f", summary_df$fruit_j_index),
      sprintf("%.4f", summary_df$fruit_auc)
    )
  ) %>%
    kable(align = c("l", "r")) %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

---

## Training Configuration

```{r training-config}
if (!is.null(params$training_config)) {
  config <- params$training_config

  tibble(
    Parameter = c("Model Version", "Pretrained Model", "Epochs", "Batch Size",
                  "Base Learning Rate", "Weight Decay", "Layer Decay"),
    Value = c(
      config$model_version %||% "N/A",
      config$pretrained_model %||% "N/A",
      as.character(config$num_epochs %||% "N/A"),
      as.character(config$batch_size %||% "N/A"),
      as.character(config$blr %||% "N/A"),
      as.character(config$weight_decay %||% "N/A"),
      as.character(config$layer_decay %||% "N/A")
    )
  ) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

---

## Test Set Metrics

### Detailed Metrics by Class

```{r test-metrics-table}
if (!is.null(params$test_metrics)) {
  params$test_metrics$metrics %>%
    mutate(across(where(is.numeric) & !matches("^n"), ~round(., 4))) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

### Confusion Matrices

```{r confusion-matrices, fig.height=4}
if (!is.null(params$test_metrics)) {
  cm_flower <- as.data.frame(params$test_metrics$confusion_matrices$flower)
  cm_fruit <- as.data.frame(params$test_metrics$confusion_matrices$fruit)

  p1 <- cm_flower %>%
    ggplot(aes(x = Predicted, y = Truth, fill = Freq)) +
    geom_tile() +
    geom_text(aes(label = format(Freq, big.mark = ",")), size = 5) +
    scale_fill_gradient(low = "white", high = "steelblue") +
    labs(title = "Flower Detection", x = "Predicted", y = "Truth") +
    theme_minimal() +
    theme(legend.position = "none")

  p2 <- cm_fruit %>%
    ggplot(aes(x = Predicted, y = Truth, fill = Freq)) +
    geom_tile() +
    geom_text(aes(label = format(Freq, big.mark = ",")), size = 5) +
    scale_fill_gradient(low = "white", high = "steelblue") +
    labs(title = "Fruit Detection", x = "Predicted", y = "Truth") +
    theme_minimal() +
    theme(legend.position = "none")

  p1 + p2
}
```

---

## Threshold Optimization

### Optimal Thresholds (Maximizing J-Index)

```{r threshold-table}
if (!is.null(params$optimal_thresholds)) {
  tibble(
    Class = c("Flower", "Fruit"),
    `Optimal Threshold` = c(
      params$optimal_thresholds$flower$threshold,
      params$optimal_thresholds$fruit$threshold
    ),
    `J-Index` = c(
      params$optimal_thresholds$flower$j_index,
      params$optimal_thresholds$fruit$j_index
    ),
    Sensitivity = c(
      params$optimal_thresholds$flower$sensitivity,
      params$optimal_thresholds$fruit$sensitivity
    ),
    Specificity = c(
      params$optimal_thresholds$flower$specificity,
      params$optimal_thresholds$fruit$specificity
    )
  ) %>%
    mutate(across(where(is.numeric), ~round(., 4))) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

### Threshold Performance Curves

```{r threshold-curves, fig.height=8}
if (!is.null(params$optimal_thresholds)) {
  # Flower threshold curve
  flower_data <- params$optimal_thresholds$flower$threshold_data %>%
    filter(.metric %in% c("j_index", "sens", "spec"))

  p1 <- ggplot(flower_data, aes(x = .threshold, y = .estimate, color = .metric)) +
    geom_line(size = 1) +
    geom_vline(xintercept = params$optimal_thresholds$flower$threshold,
               linetype = "dashed", color = "red") +
    scale_color_manual(values = c("j_index" = "purple", "sens" = "blue", "spec" = "green"),
                       labels = c("j_index" = "J-Index", "sens" = "Sensitivity", "spec" = "Specificity")) +
    labs(title = "Flower Detection", x = "Threshold", y = "Metric Value", color = "Metric") +
    theme_minimal()

  # Fruit threshold curve
  fruit_data <- params$optimal_thresholds$fruit$threshold_data %>%
    filter(.metric %in% c("j_index", "sens", "spec"))

  p2 <- ggplot(fruit_data, aes(x = .threshold, y = .estimate, color = .metric)) +
    geom_line(size = 1) +
    geom_vline(xintercept = params$optimal_thresholds$fruit$threshold,
               linetype = "dashed", color = "red") +
    scale_color_manual(values = c("j_index" = "purple", "sens" = "blue", "spec" = "green"),
                       labels = c("j_index" = "J-Index", "sens" = "Sensitivity", "spec" = "Specificity")) +
    labs(title = "Fruit Detection", x = "Threshold", y = "Metric Value", color = "Metric") +
    theme_minimal()

  p1 / p2
}
```

### Threshold Performance Plot

This plot shows how different metrics vary across threshold values.

```{r threshold-performance-plot, fig.width=10, fig.height=5}
if (!is.null(params$plot_threshold_performance) && file.exists(params$plot_threshold_performance)) {
  knitr::include_graphics(params$plot_threshold_performance)
}
```

---

## ROC Curves

```{r roc-curves, fig.height=5}
if (!is.null(params$all_predictions)) {
  test_data <- params$all_predictions %>%
    filter(partition == "testing")

  # Calculate ROC curves
  roc_flower <- yardstick::roc_curve(test_data, flower, .pred_flower, event_level = "first")
  roc_fruit <- yardstick::roc_curve(test_data, fruit, .pred_fruit, event_level = "first")

  roc_combined <- bind_rows(
    roc_flower %>% mutate(class = "Flower"),
    roc_fruit %>% mutate(class = "Fruit")
  )

  ggplot(roc_combined, aes(x = 1 - specificity, y = sensitivity, color = class)) +
    geom_path(size = 1) +
    geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "gray50") +
    scale_color_manual(values = c("Flower" = "steelblue", "Fruit" = "coral")) +
    labs(
      title = "ROC Curves",
      x = "1 - Specificity (False Positive Rate)",
      y = "Sensitivity (True Positive Rate)",
      color = "Class"
    ) +
    coord_equal() +
    theme_minimal()
}
```

---

## Conformal Prediction Analysis

### Mondrian Coverage Check (Split by True Label)

Conformal prediction should achieve approximately (1 - alpha) coverage at significance level alpha.
For Mondrian conformal prediction, coverage is checked **separately** for each true label (detected vs not detected).

```{r coverage-table}
if (!is.null(params$conformal_coverage)) {
  params$conformal_coverage %>%
    mutate(
      coverage_diff = coverage - expected_coverage,
      true_label = ifelse(true_label == "1", "Detected", "Not Detected"),
      across(where(is.numeric), ~round(., 4))
    ) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

```{r coverage-plot, fig.width=10, fig.height=5}
if (!is.null(params$plot_conformal_coverage) && file.exists(params$plot_conformal_coverage)) {
  knitr::include_graphics(params$plot_conformal_coverage)
}
```

### Alpha Cutoff Sensitivity Analysis

This analysis shows how different alpha cutoffs affect the trade-off between data retention and accuracy.

```{r alpha-analysis-plot, fig.height=8}
if (!is.null(params$alpha_analysis)) {
  # Plot accuracy vs percent removed
  p1 <- ggplot(params$alpha_analysis, aes(x = pct_removed, y = accuracy, color = class)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    scale_color_manual(values = c("flower" = "steelblue", "fruit" = "coral")) +
    labs(
      title = "Accuracy vs Data Removed",
      x = "Percent Removed as Uncertain (%)",
      y = "Accuracy",
      color = "Class"
    ) +
    theme_minimal()

  # Plot J-index vs alpha
  p2 <- ggplot(params$alpha_analysis, aes(x = alpha, y = j_index, color = class)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    scale_color_manual(values = c("flower" = "steelblue", "fruit" = "coral")) +
    labs(
      title = "J-Index vs Alpha Cutoff",
      x = "Alpha",
      y = "J-Index",
      color = "Class"
    ) +
    theme_minimal()

  # Plot PPV vs percent removed
  p3 <- ggplot(params$alpha_analysis, aes(x = pct_removed, y = ppv, color = class)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    scale_color_manual(values = c("flower" = "steelblue", "fruit" = "coral")) +
    labs(
      title = "PPV vs Data Removed",
      x = "Percent Removed as Uncertain (%)",
      y = "Positive Predictive Value",
      color = "Class"
    ) +
    theme_minimal()

  # Plot percent removed vs alpha
  p4 <- ggplot(params$alpha_analysis, aes(x = alpha, y = pct_removed, color = class)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    scale_color_manual(values = c("flower" = "steelblue", "fruit" = "coral")) +
    labs(
      title = "Data Removed vs Alpha Cutoff",
      x = "Alpha",
      y = "Percent Removed (%)",
      color = "Class"
    ) +
    theme_minimal()

  (p1 + p2) / (p3 + p4)
}
```

### Alpha Analysis Table (Combined Approach)

```{r alpha-table}
if (!is.null(params$alpha_analysis)) {
  params$alpha_analysis %>%
    mutate(across(where(is.numeric) & !matches("^n"), ~round(., 4))) %>%
    arrange(class, alpha) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"), font_size = 11) %>%
    scroll_box(height = "400px")
}
```

---

## Factorial Alpha Optimization (NEW APPROACH)

### Overview

**Problem with Independent Optimization:**
The previous approach optimized positive and negative alpha cutoffs independently, which is **fundamentally flawed** because:

- **PPV depends on BOTH cutoffs** through false positive rate
- **Data loss depends on BOTH cutoffs** (a sample may be kept by one criterion but removed by another)
- Independent optimization ignores critical interactions between the two hypotheses

**Factorial Approach:**
Test all combinations of `(alpha_pos, alpha_neg)` to find the true Pareto frontier of PPV vs. data loss trade-offs.

**Filtering Logic (Conservative):**

- **Keep:** EXACTLY ONE p-value exceeds threshold → confident about one class
- **Remove (uncertain):** BOTH p-values BELOW thresholds → uncertain about both
- **Remove (contradictory):** BOTH p-values ABOVE thresholds → confident about both (contradictory)

**Tested:** `r length(unique(params$alpha_analysis_factorial$alpha_pos))` × `r length(unique(params$alpha_analysis_factorial$alpha_neg))` = `r length(unique(params$alpha_analysis_factorial$alpha_pos)) * length(unique(params$alpha_analysis_factorial$alpha_neg))` combinations per class

### Optimal Alpha Candidates

Four optimization methods identify different points on the Pareto frontier:

1. **Conservative:** Highest PPV within 20% data loss constraint
2. **Efficiency Ratio:** Where ΔPPV/Δdata_loss drops below 0.5
3. **Inflection Point:** Where second derivative = 0 (diminishing returns)
4. **Elbow:** Maximum distance to line connecting first and last Pareto points

```{r candidates-table}
if (!is.null(params$optimal_alpha_candidates)) {
  params$optimal_alpha_candidates %>%
    select(class, method, alpha_pos, alpha_neg, dqi, sensitivity, ppv, npv, accuracy, j_index, pct_detected_removed) %>%
    mutate(across(where(is.numeric) & !matches("alpha|pct"), ~round(., 4))) %>%
    mutate(pct_detected_removed = round(pct_detected_removed, 2)) %>%
    rename(`Det. Loss %` = pct_detected_removed) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

### Contour Plots: PPV Optimization

These plots show PPV across all `(alpha_pos, alpha_neg)` combinations. Red points mark optimal selections from each method. White dashed lines show data loss contours.

```{r ppv-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_ppv_flower) && file.exists(params$plot_factorial_ppv_flower) &&
    !is.null(params$plot_factorial_ppv_fruit) && file.exists(params$plot_factorial_ppv_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_ppv_flower, params$plot_factorial_ppv_fruit))
}
```

### Contour Plots: NPV Optimization

```{r npv-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_npv_flower) && file.exists(params$plot_factorial_npv_flower) &&
    !is.null(params$plot_factorial_npv_fruit) && file.exists(params$plot_factorial_npv_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_npv_flower, params$plot_factorial_npv_fruit))
}
```

### Contour Plots: Accuracy Optimization

```{r accuracy-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_accuracy_flower) && file.exists(params$plot_factorial_accuracy_flower) &&
    !is.null(params$plot_factorial_accuracy_fruit) && file.exists(params$plot_factorial_accuracy_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_accuracy_flower, params$plot_factorial_accuracy_fruit))
}
```

### Contour Plots: J-Index Optimization

```{r jindex-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_jindex_flower) && file.exists(params$plot_factorial_jindex_flower) &&
    !is.null(params$plot_factorial_jindex_fruit) && file.exists(params$plot_factorial_jindex_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_jindex_flower, params$plot_factorial_jindex_fruit))
}
```

### Contour Plots: DQI (Detection Quality Index) Optimization

DQI = PPV + Sensitivity - 1. This is the metric used for optimization in this pipeline, as it balances positive predictive value with detection completeness.

```{r dqi-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_dqi_flower) && file.exists(params$plot_factorial_dqi_flower) &&
    !is.null(params$plot_factorial_dqi_fruit) && file.exists(params$plot_factorial_dqi_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_dqi_flower, params$plot_factorial_dqi_fruit))
}
```

### Contour Plots: Overall Data Loss

```{r dataloss-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_dataloss_flower) && file.exists(params$plot_factorial_dataloss_flower) &&
    !is.null(params$plot_factorial_dataloss_fruit) && file.exists(params$plot_factorial_dataloss_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_dataloss_flower, params$plot_factorial_dataloss_fruit))
}
```

### Contour Plots: Detection Data Loss

This shows the percentage of **true detections** (presence-only records) that would be removed at each alpha combination. For presence-only data like phenology detections, losing true detections is more costly than losing non-detections.

```{r det-dataloss-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_det_dataloss_flower) && file.exists(params$plot_factorial_det_dataloss_flower) &&
    !is.null(params$plot_factorial_det_dataloss_fruit) && file.exists(params$plot_factorial_det_dataloss_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_det_dataloss_flower, params$plot_factorial_det_dataloss_fruit))
}
```

### Contour Plots: Non-Detection Data Loss

This shows the percentage of **non-detections** that would be removed. Since we use a presence-only approach (only reporting detections), losing non-detections has less impact on downstream analyses.

```{r nondet-dataloss-contours, fig.width=8, fig.height=12}
if (!is.null(params$plot_factorial_nondet_dataloss_flower) && file.exists(params$plot_factorial_nondet_dataloss_flower) &&
    !is.null(params$plot_factorial_nondet_dataloss_fruit) && file.exists(params$plot_factorial_nondet_dataloss_fruit)) {
  knitr::include_graphics(c(params$plot_factorial_nondet_dataloss_flower, params$plot_factorial_nondet_dataloss_fruit))
}
```

### 2D Density of Conformal P-Values

This plot shows the joint distribution of conformal p-values for the "detected" and "not detected" hypotheses. Points in the lower-right corner indicate samples that conform strongly to the "detected" class, while points in the upper-left conform to "not detected". Points along the diagonal indicate uncertainty.

```{r conformal-pvalue-density, fig.width=14, fig.height=6}
if (!is.null(params$plot_conformal_pvalue_density) && file.exists(params$plot_conformal_pvalue_density)) {
  knitr::include_graphics(params$plot_conformal_pvalue_density)
}
```

### Pareto Frontier and Elbow Method

This plot shows the DQI vs Detection Data Loss trade-off curve. The Pareto frontier (blue line) shows the optimal combinations - points where you cannot improve DQI without increasing data loss or vice versa. The elbow method finds the point with maximum perpendicular distance from the line connecting the endpoints.

```{r pareto-elbow, fig.width=14, fig.height=6}
if (!is.null(params$plot_pareto_elbow) && file.exists(params$plot_pareto_elbow)) {
  knitr::include_graphics(params$plot_pareto_elbow)
}
```

### Conformal P-Value Calibration Curve

This plot shows how conformal p-values change across the full range of possible model outputs (0 to 1). It visualizes the relationship between model probability and conformal p-values, helping understand how the conformal prediction converts raw probabilities into coverage-guaranteed p-values.

```{r conformal-calibration-curve, fig.width=14, fig.height=6}
if (!is.null(params$plot_conformal_calibration_curve) && file.exists(params$plot_conformal_calibration_curve)) {
  knitr::include_graphics(params$plot_conformal_calibration_curve)
}
```

### Ambiguity Diagnostic

Breakdown of why samples were removed (uncertain vs. contradictory):

```{r ambiguity-diagnostic}
if (!is.null(params$optimal_alpha_candidates)) {
  # Get conservative method results (highest DQI)
  conservative_candidates <- params$optimal_alpha_candidates %>%
    filter(method == "conservative")

  ambiguity_summary <- conservative_candidates %>%
    select(class, alpha_pos, alpha_neg, n_total, n_kept, n_removed, n_both_low, n_both_high) %>%
    mutate(
      pct_both_low = round(100 * n_both_low / n_total, 2),
      pct_both_high = round(100 * n_both_high / n_total, 2),
      pct_kept = round(100 * n_kept / n_total, 2)
    ) %>%
    select(class, alpha_pos, alpha_neg, n_total, n_kept, pct_kept,
           n_both_low, pct_both_low, n_both_high, pct_both_high)

  kable(ambiguity_summary) %>%
    kable_styling(bootstrap_options = c("striped", "hover")) %>%
    add_header_above(c(" " = 3, " " = 3, "Uncertain (both low)" = 2, "Contradictory (both high)" = 2))
}
```

**Interpretation:**

- **n_both_low (Uncertain):** Both p-values below thresholds → model not confident about either hypothesis
- **n_both_high (Contradictory):** Both p-values above thresholds → model confident about BOTH hypotheses (should never happen theoretically, but can occur with miscalibration)

---

## Accuracy-Based Buffer Zones (Equivocal Zone Analysis)

This analysis uses the original approach from the paper to find buffer zones where model predictions are unreliable. It is simpler and more intuitive than conformal prediction factorial optimization.

**Method:**
1. Divide model output (0-1) into 100 intervals using `santoku::chop_evenly()`
2. Calculate accuracy within each interval using `yardstick::accuracy()`
3. Apply LOESS smoothing to handle sparse intervals (especially important for leaf model)
4. Find intervals where smoothed accuracy ≤ 75%
5. Those intervals define the buffer zone (equivocal/uncertain predictions)

The buffer zone represents model outputs where predictions are unreliable and should be marked as "Equivocal" rather than "Detected" or "Not Detected".

### Combined View (Both Classes)

```{r equivocal-zone-combined, fig.width=10, fig.height=8}
if (!is.null(params$plot_equivocal_zone_combined) && file.exists(params$plot_equivocal_zone_combined)) {
  knitr::include_graphics(params$plot_equivocal_zone_combined)
}
```

### Buffer Zone Summary

```{r buffer-summary-table}
if (!is.null(params$accuracy_buffer_flower_overall)) {
  tibble::tibble(
    Class = c("Flower", "Flower", "Fruit", "Fruit"),
    Metric = c("Overall Accuracy", "PPV/NPV", "Overall Accuracy", "PPV/NPV"),
    Threshold = c(
      params$accuracy_buffer_flower_overall$optimal_threshold,
      params$accuracy_buffer_flower_ppv_npv$optimal_threshold,
      params$accuracy_buffer_fruit_overall$optimal_threshold,
      params$accuracy_buffer_fruit_ppv_npv$optimal_threshold
    ),
    `Buffer Lower` = c(
      params$accuracy_buffer_flower_overall$buffer_lower,
      params$accuracy_buffer_flower_ppv_npv$buffer_lower,
      params$accuracy_buffer_fruit_overall$buffer_lower,
      params$accuracy_buffer_fruit_ppv_npv$buffer_lower
    ),
    `Buffer Upper` = c(
      params$accuracy_buffer_flower_overall$buffer_upper,
      params$accuracy_buffer_flower_ppv_npv$buffer_upper,
      params$accuracy_buffer_fruit_overall$buffer_upper,
      params$accuracy_buffer_fruit_ppv_npv$buffer_upper
    )
  ) %>%
    dplyr::mutate(
      `Equivocal Zone` = sprintf("[%.2f, %.2f]",
                                 Threshold - `Buffer Lower`,
                                 Threshold + `Buffer Upper`)
    ) %>%
    knitr::kable(digits = 3) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

**Original Paper Buffer Values (for comparison):**
- Flower: threshold=0.84, buffer=[0.56, 0.01] → equivocal zone [0.28, 0.85]
- Fruit: threshold=0.53, buffer=[0.30, 0.22] → equivocal zone [0.23, 0.75]

### Method Comparison: Overall Accuracy vs PPV/NPV

Two accuracy metrics are compared:
- **Overall Accuracy:** (TP + TN) / Total within each interval - the classic approach
- **PPV/NPV:** Use PPV for intervals above threshold, NPV for intervals below - more directly relevant to the decision being made

#### Flower
```{r accuracy-buffer-flower, fig.width=14, fig.height=7}
if (!is.null(params$plot_accuracy_buffer_flower) && file.exists(params$plot_accuracy_buffer_flower)) {
  knitr::include_graphics(params$plot_accuracy_buffer_flower)
}
```

#### Fruit
```{r accuracy-buffer-fruit, fig.width=14, fig.height=7}
if (!is.null(params$plot_accuracy_buffer_fruit) && file.exists(params$plot_accuracy_buffer_fruit)) {
  knitr::include_graphics(params$plot_accuracy_buffer_fruit)
}
```

### Interpretation

The accuracy-based buffer zone approach is:
- **Simpler:** No complex 2D optimization required
- **More Intuitive:** Directly shows where the model is unreliable
- **Proven:** This is the method used in the original paper
- **Robust:** LOESS smoothing handles sparse data gracefully

When using `probably::make_two_class_pred()`, the buffer parameter `c(lower, upper)` defines how far below and above the threshold to mark predictions as "Equivocal".

---

### Multi-Cutoff Sensitivity Analysis

This analysis tests multiple accuracy cutoffs (75% to 95% by 2%) to understand the tradeoff between prediction reliability (higher cutoff = more reliable predictions kept) and data loss (larger buffer zone = more samples removed).

**Key insights:**
- Higher cutoffs are **stricter**: only intervals with very high accuracy remain outside the buffer
- Stricter cutoffs lead to **larger buffer zones** and thus **more data loss**
- Data loss is broken down by detection status (truth=1 vs truth=0) to show which class is more affected

```{r multi-cutoff-plot, fig.width=10, fig.height=10}
if (!is.null(params$plot_multi_cutoff_dataloss) && file.exists(params$plot_multi_cutoff_dataloss)) {
  knitr::include_graphics(params$plot_multi_cutoff_dataloss)
}
```

```{r multi-cutoff-table}
if (!is.null(params$multi_cutoff_flower) && !is.null(params$multi_cutoff_fruit)) {
  dplyr::bind_rows(params$multi_cutoff_flower, params$multi_cutoff_fruit) %>%
    dplyr::select(class, cutoff, buffer_lower, buffer_upper,
                  pct_data_loss, pct_detected_loss, pct_not_detected_loss) %>%
    dplyr::mutate(cutoff = scales::percent(cutoff, accuracy = 1)) %>%
    knitr::kable(
      digits = 2,
      col.names = c("Class", "Cutoff", "Buffer Lower", "Buffer Upper",
                    "Total Loss %", "Detected Loss %", "Not Detected Loss %"),
      caption = "Buffer zone size and data loss at different accuracy cutoffs"
    )
}
```

---

## Legacy Independent Analysis (DEPRECATED)

These sections show the flawed independent optimization approach for comparison. **Do not use these results for inference.**

### Positive Detection Analysis (Independent Optimization)

This analysis optimizes alpha cutoffs **specifically for positive (detected) predictions**, measuring PPV vs data removal.
Higher alpha means more stringent filtering (removing more data), which improves PPV but reduces coverage.

**CAUTION:** This approach ignores the negative cutoff's effect on false positives and data retention.

```{r positive-analysis-plot, fig.width=10, fig.height=5}
if (!is.null(params$plot_conformal_positive) && file.exists(params$plot_conformal_positive)) {
  knitr::include_graphics(params$plot_conformal_positive)
}
```

```{r positive-analysis-table}
if (!is.null(params$alpha_analysis_positive)) {
  params$alpha_analysis_positive %>%
    mutate(
      across(where(is.numeric) & !matches("^n|pct_removed"), ~round(., 4)),
      across(matches("pct_removed"), ~round(., 2))
    ) %>%
    select(class, alpha, pct_removed, ppv, sensitivity, specificity) %>%
    arrange(class, alpha) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

### Negative Detection Analysis (Independent Optimization)

This analysis optimizes alpha cutoffs **specifically for negative (not detected) predictions**, measuring NPV vs data removal.
Higher alpha means more stringent filtering (removing more data), which improves NPV but reduces coverage.

**CAUTION:** This approach ignores the positive cutoff's effect on false negatives and data retention.

```{r negative-analysis-plot, fig.width=10, fig.height=5}
if (!is.null(params$plot_conformal_negative) && file.exists(params$plot_conformal_negative)) {
  knitr::include_graphics(params$plot_conformal_negative)
}
```

```{r negative-analysis-table}
if (!is.null(params$alpha_analysis_negative)) {
  params$alpha_analysis_negative %>%
    mutate(
      across(where(is.numeric) & !matches("^n|pct_removed"), ~round(., 4)),
      across(matches("pct_removed"), ~round(., 2))
    ) %>%
    select(class, alpha, pct_removed, npv, sensitivity, specificity) %>%
    arrange(class, alpha) %>%
    kable() %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

---

## Prediction Distributions

```{r prediction-distributions, fig.height=6}
if (!is.null(params$all_predictions)) {
  test_data <- params$all_predictions %>%
    filter(partition == "testing")

  # Flower distribution
  p1 <- ggplot(test_data, aes(x = .pred_flower, fill = flower)) +
    geom_histogram(bins = 50, alpha = 0.7, position = "identity") +
    scale_fill_manual(values = c("1" = "steelblue", "0" = "gray70"),
                      labels = c("1" = "Detected", "0" = "Not Detected")) +
    geom_vline(xintercept = params$optimal_thresholds$flower$threshold,
               linetype = "dashed", color = "red", size = 1) +
    labs(title = "Flower Prediction Distribution", x = "Predicted Probability",
         y = "Count", fill = "Truth") +
    theme_minimal()

  # Fruit distribution
  p2 <- ggplot(test_data, aes(x = .pred_fruit, fill = fruit)) +
    geom_histogram(bins = 50, alpha = 0.7, position = "identity") +
    scale_fill_manual(values = c("1" = "coral", "0" = "gray70"),
                      labels = c("1" = "Detected", "0" = "Not Detected")) +
    geom_vline(xintercept = params$optimal_thresholds$fruit$threshold,
               linetype = "dashed", color = "red", size = 1) +
    labs(title = "Fruit Prediction Distribution", x = "Predicted Probability",
         y = "Count", fill = "Truth") +
    theme_minimal()

  p1 / p2
}
```

---

## Final Model Evaluation Summary

This section presents the final evaluation of the trained model on the held-out **test set**, comparing performance before and after removing predictions in the buffer zone (equivocal/uncertain region).

### Final Buffer Zone Parameters

The buffer zones were determined using **80% accuracy cutoff** with the overall accuracy method.

```{r final-buffer-params}
if (!is.null(params$test_evaluation_summary)) {
  # Extract buffer parameters from the accuracy_buffer results
  flower_params <- params$accuracy_buffer_flower_overall
  fruit_params <- params$accuracy_buffer_fruit_overall

  tibble::tibble(
    Class = c("Flower", "Fruit"),
    Threshold = c(flower_params$optimal_threshold, fruit_params$optimal_threshold),
    `Buffer Lower` = c(flower_params$buffer_lower, fruit_params$buffer_lower),
    `Buffer Upper` = c(flower_params$buffer_upper, fruit_params$buffer_upper),
    `Equivocal Zone` = c(
      sprintf("[%.3f, %.3f]",
              flower_params$optimal_threshold - flower_params$buffer_lower,
              flower_params$optimal_threshold + flower_params$buffer_upper),
      sprintf("[%.3f, %.3f]",
              fruit_params$optimal_threshold - fruit_params$buffer_lower,
              fruit_params$optimal_threshold + fruit_params$buffer_upper)
    )
  ) %>%
    knitr::kable(digits = 3, caption = "Final buffer zone parameters (80% accuracy cutoff)") %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)
}
```

### Test Set Performance: Before vs After Buffer Zone Filtering

```{r test-evaluation-table}
if (!is.null(params$test_evaluation_summary)) {
  params$test_evaluation_summary %>%
    dplyr::mutate(
      across(where(is.numeric) & !matches("^n$|pct"), ~round(., 4)),
      pct_data_loss = round(pct_data_loss, 2)
    ) %>%
    dplyr::select(class, filter, n, pct_data_loss, accuracy, ppv, npv,
                  sensitivity, specificity, j_index, dqi) %>%
    knitr::kable(
      col.names = c("Class", "Filter", "N", "Data Loss %", "Accuracy", "PPV", "NPV",
                    "Sensitivity", "Specificity", "J-Index", "DQI"),
      caption = "Test set performance before and after buffer zone filtering"
    ) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
}
```

### Key Takeaways

```{r test-evaluation-summary-text, results='asis'}
if (!is.null(params$test_evaluation_summary)) {
  summary_data <- params$test_evaluation_summary

  # Calculate improvements
  flower_before <- summary_data %>% filter(class == "flower", filter == "All test data")
  flower_after <- summary_data %>% filter(class == "flower", filter == "Buffer zone removed")
  fruit_before <- summary_data %>% filter(class == "fruit", filter == "All test data")
  fruit_after <- summary_data %>% filter(class == "fruit", filter == "Buffer zone removed")

  cat("**Flower predictions:**\n\n")
  cat(sprintf("- Accuracy improved from %.1f%% to %.1f%% (+%.1f%%)\n",
              flower_before$accuracy * 100, flower_after$accuracy * 100,
              (flower_after$accuracy - flower_before$accuracy) * 100))
  cat(sprintf("- PPV improved from %.1f%% to %.1f%% (+%.1f%%)\n",
              flower_before$ppv * 100, flower_after$ppv * 100,
              (flower_after$ppv - flower_before$ppv) * 100))
  cat(sprintf("- Data loss: %.1f%% of test samples removed\n\n", flower_after$pct_data_loss))

  cat("**Fruit predictions:**\n\n")
  cat(sprintf("- Accuracy improved from %.1f%% to %.1f%% (+%.1f%%)\n",
              fruit_before$accuracy * 100, fruit_after$accuracy * 100,
              (fruit_after$accuracy - fruit_before$accuracy) * 100))
  cat(sprintf("- PPV improved from %.1f%% to %.1f%% (+%.1f%%)\n",
              fruit_before$ppv * 100, fruit_after$ppv * 100,
              (fruit_after$ppv - fruit_before$ppv) * 100))
  cat(sprintf("- Data loss: %.1f%% of test samples removed\n", fruit_after$pct_data_loss))
}
```

---

## Session Info

```{r session-info}
sessionInfo()
```

---

*Report generated on `r Sys.time()`*
